InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-28 paper.tex
add initial text

>>>>

The \textbf{ai-image-det-resnet18} model is a community made, fine tuned, resnet18 based, pretrained image detection model. For finetuneing the author kgmann on Hugging Face used the AI or Not dataset. ResNet-18 is a convolutional neural network that is 18 layers deep. It got pretrained by over a million images from the ImageNet database. \cite{https://arxiv.org/pdf/1512.03385.pdf}
